%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%   CAPTER 1   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
\label{chap:introduction}

Introduction to the overall topic.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%   SECTION   %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Statement}
\label{sec:intro:probstatement}

The problem space is definced by the following.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%   SECTION   %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Contributions}
\label{sec:intro:contrib}


Why is this an important problem ?
%

In summary, the main contributions of this thesis are:

\begin{itemize}
\item{\bf Tools}
  \begin{itemize}
    \item {\it Design and implementation of measurement tool \textit{Moni} to collect information:} In order to be able to analyze the impact, we needed direct measurements from the lower layer.
  \end{itemize}
\item {\bf Algorithm \& Implementation}
 	\begin{itemize}
    	\item {\it Linux sublayer extension to enable allocation per packet:} To enable setting per packet we extend Linux subsystem.
    	\item {\it Design and implementation of our joint controller}: We designed and implemented a joint controller within the Linux kernel.
	\end{itemize}
\item {\bf Measurements}
  \begin{itemize}
      \item {\it Feasibility of parameter control and its constraints:} We explore the capabilities of today's hardware and explored the ability to set different parameters.
	    \item {\it Validation and Performance Analysis:} We perform several validation experiments that confirm trobust operation.
  \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%   SECTION   %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Thesis outline}
\label{sec:intro:outline}

The rest of this thesis is organized as follows:

\begin{compactitem}
  \item In Chapter 2, we discuss the theoretical and practical approaches.
  \item In Chapter 3, we present our Testbed in detail.
  \item In Chapter 4, we present our in-kernel monitoring tool .
  \item In Chapter 5, we present the design, the Linux implementation, the validation and performance evaluation of our controller.
  \item In Chapter 6, we summarize the contributions and limitations of our systems, and outline several directions for future work.
\end{compactitem}